\emeszida

### 2024-03-29 sigbovik/paper.tex
Remove unneeded citation

\paragraph{Arguments}
An instruction's arguments may be numbers, register addresses, or a combination of the two. Numbers are encoded following standard Babylonian conventions \cite{TODO}, with \textcuneiform{𒋙} denoting the radix point which separates the integer part from a following fraction. There is an explicit representation for zero (\textcuneiform{𒑱}), making these tablets some of the earliest unambigiuous examples of the mathematical concept of zero.

>>>>

\paragraph{Arguments}
An instruction's arguments may be numbers, register addresses, or a combination of the two. Numbers are encoded following standard Babylonian conventions, with \textcuneiform{𒋙} denoting the radix point which separates the integer part from a following fraction. There is an explicit representation for zero (\textcuneiform{𒑱}), making these tablets some of the earliest unambigiuous examples of the mathematical concept of zero.
